---
title: "Untitled"
format: html
execute: 
  warning: false 
  message: false
---

## Quarto

Quarto enables yo

#set up

```{r liraries}
library(tidyverse)
library(here)
library(lterdatasampler)

library(performance)
library(broom)
library(flextable)
library(ggeffects)
library(car)
library(naniar)
```

#linear models

How does stem length *predict* stem dry mass?

```{r filtering-data}
maples_data <- hbr_maples %>% 
  filter(year == 2003 & watershed =="Reference")#to replace & or ,

```

Visualizing missing data:

```{r missing-data-vis}
gg_miss_var(maples_data)
```

Create an exploratory data visualization:

```{r explore-data-vis}
ggplot(data=maples_data, aes(x = stem_length, y = stem_dry_mass))+ 
  geom_point()
```

Lets try a model:

```{r linear-model-maples}
maples_model <- lm(stem_dry_mass ~ stem_length, data = maples_data)
maples_model
```

Check assumptions:

1.  Linear relationship between variables: yes! (used the exploratory data visualization to check that)
2.  independence of errors: yes! (making that assumption based on how the data was collected)
3.  homeskedasticity of errors: yes! (making the decision from residuals vs fitted plot/scale - location plots)
4.   normally distributed errors: yes! (looking at QQ plot of residuals)

```{r checking-assumptions}
par(mfrow = c(2, 2))
plot(maples_model)


```

turning off the 2x2 grid

```{r turning-off-the-grid, results = FALSE}
dev.off()
```

u to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
